---
title: "2021-09-24_simulations_denseBMA1"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(BayesGPfit)
# rpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/sim_result"
dpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/data"
dpath2 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-26_simulations_sparseBMA1"
rpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/sim_result"
rpath2 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-26_simulations_sparseBMA1/sim_result2"
num_region = 4
side = 64
region_idx = vector("list",num_region)
grids = GP.generate.grids(d=2L,num_grids=side)
grids = as.data.frame(grids)
library(ggplot2)
library(viridis)
source("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/Soft_thresholding/STGP_code/Mediation_Analysis/BMA_pkg/R/MA_data_generation.R", echo=TRUE)
idx_mat = matrix(1:(side*side),ncol = num_region)
idx_matr = matrix(1:(side*side),ncol = 64)
p_length = NULL
region_idx[[1]] = intersect(idx_matr[1:32,],idx_mat[,1:2])
region_idx[[2]] = intersect(idx_matr[33:64,],idx_mat[,1:2])
region_idx[[3]] = intersect(idx_matr[1:32,],idx_mat[,3:4])
region_idx[[4]] = intersect(idx_matr[33:64,],idx_mat[,3:4])
basis_sq = generate_sq_basis(grids, region_idx,a = 0.01,b = 10)
```



```{r total, include = FALSE}
apath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/"
result1.1 <- readRDS(file.path(apath,"2021-09-24_simulations_denseBMA1/analysis_result_delta01.rds"))
result1.2 <- readRDS(file.path(apath,"2021-09-24_simulations_denseBMA1/analysis_result_delta001.rds"))
result2.1 <- readRDS(file.path(apath,"2021-09-26_simulations_sparseBMA1/analysis_result_delta01.rds"))
result2.2 <- readRDS(file.path(apath,"2021-09-26_simulations_sparseBMA1/analysis_result_delta001.rds"))

tab_beta = matrix(NA,nrow = 4,ncol=8)
colnames(tab_beta) = c("Analysis","FDR_no_control","Precision_no_control","Power_no_control",
                       "CoverageProb",
                       "FDR_control","Precision_control","Power_control")
tab_beta[,1] = c("dense:delta=0.1","dense:delta=0.01",
                 "sparse:delta=0.1","sparse:delta=0.01")
tab_alpha = tab_total = tab_beta


analyze = function(result){
  re1 = NULL
  for(i in 1:3){
    re1 = rbind(re1,apply(result[[i]],2,mean))
  }
  re_all = rep(NA,7)
  re_all[1:3] = re1[,1]
  re_all[5:7] = re1[,2]
  re_all[4] = mean(result[[4]])
  re_all = round(re_all,digits = 4)
  return(re_all)
}

tab_beta[1,2:8] = analyze(result1.1[1:4])
tab_alpha[1,2:8] = analyze(result1.1[5:8])
tab_total[1,2:8] = analyze(result1.1[9:12])

tab_beta[2,2:8] = analyze(result1.2[1:4])
tab_alpha[2,2:8] = analyze(result1.2[5:8])
tab_total[2,2:8] = analyze(result1.2[9:12])

tab_beta[3,2:8] = analyze(result2.1[1:4])
tab_alpha[3,2:8] = analyze(result2.1[5:8])
tab_total[3,2:8] = analyze(result2.1[9:12])

tab_beta[4,2:8] = analyze(result2.2[1:4])
tab_alpha[4,2:8] = analyze(result2.2[5:8])
tab_total[4,2:8] = analyze(result2.2[9:12])


```
# Explain on the row names in the following table

I run 2 set of simulations, each with 100 replicates, one replicate being a dataset of n=1000. The true image consists of 64 x 64 pixels, evenly divided into 4 regions, the number of basis functions for each region is 231. Total p = 4096, total L= 924.

In the first simulation, there is ONE cluster of signals within each region for both true alpha and beta. This will be denoted as "dense" in the result table.

```{r}
datsim = readRDS(file.path(dpath,"data1.rds"))
ggplot(grids) + geom_point(aes(x1, x2, color = datsim$beta_test_ST),shape=15,size=2) + scale_color_viridis()
ggplot(grids) + geom_point(aes(x1, x2, color = datsim$alpha_test_ST),shape=15,size=2) + scale_color_viridis()
```

In the first simulation, there is TWO cluster of signals within each region for both true alpha and beta. This will be denoted as "sparse" in the result table.
```{r}
datsim2 = readRDS(file.path(dpath2,"data1.rds"))
ggplot(grids) + geom_point(aes(x1, x2, color = datsim2$beta_test_ST),shape=15,size=2) + scale_color_viridis()
ggplot(grids) + geom_point(aes(x1, x2, color = datsim2$alpha_test_ST),shape=15,size=2) + scale_color_viridis()
```

In addition, in the FDR control procedure, the value delta affects the controlled FDR, so is the sample size. In the result below, I reported 2 result for each simulation when setting delta to 0.1 and 0.01.
The number of samples used for beta is 2000, and for alpha is 200. For beta, the MCMC sample is thinned, taken once in every 10 samples.

# result for beta
```{r}
knitr::kable(t(tab_beta))
```

# result for alpha
```{r}
knitr::kable(t(tab_alpha))
```

# result for total indirect effect
```{r}
knitr::kable(t(tab_total))
```

# illustration on the posterior mean
Dense case

```{r}
n_rep=1
  Y_result = readRDS(file.path(rpath,paste("simy",n_rep,".rds",sep="") ))
  datsim = readRDS(file.path(dpath,paste("data",n_rep,".rds",sep="") ))
  n_mcmc = dim(Y_result$theta_beta_mcmc_thin)[2]
  theta_sample = Y_result$theta_beta_mcmc_thin[,ceiling(n_mcmc*0.8):n_mcmc]
  beta_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_beta = apply(beta_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_beta),shape=15,size=2) + scale_color_viridis()
```

```{r}
  M_result = readRDS(file.path(rpath,paste("simm",n_rep,".rds",sep="") ))
  n_mcmc = dim(M_result$theta_alpha_mcmc)[2]
  theta_sample = M_result$theta_alpha_mcmc[,ceiling(n_mcmc*0.9):n_mcmc]
  alpha_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_alpha = apply(alpha_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_alpha),shape=15,size=2) + scale_color_viridis()
```

Sparse case


```{r}
  Y_result = readRDS(file.path(rpath2,paste("simy",n_rep,".rds",sep="") ))
  datsim = readRDS(file.path(dpath2,paste("data",n_rep,".rds",sep="") ))
  n_mcmc = dim(Y_result$theta_beta_mcmc_thin)[2]
  theta_sample = Y_result$theta_beta_mcmc_thin[,ceiling(n_mcmc*0.8):n_mcmc]
  beta_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_beta = apply(beta_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_beta),shape=15,size=2) + scale_color_viridis()
```

```{r}
  M_result = readRDS(file.path(rpath2,paste("simm",n_rep,".rds",sep="") ))
  n_mcmc = dim(M_result$theta_alpha_mcmc)[2]
  theta_sample = M_result$theta_alpha_mcmc[,ceiling(n_mcmc*0.9):n_mcmc]
  alpha_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_alpha = apply(alpha_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_alpha),shape=15,size=2) + scale_color_viridis()
```
