---
title: "2021-10-07_simulations_SME"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(BayesGPfit)
# rpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/sim_result"
dpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/data"
dpath2 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-26_simulations_sparseBMA1"
dpath3 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/data4"
dpath4 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_2"
dpath4_3 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_3"
rpath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-24_simulations_denseBMA1/sim_result"
rpath2 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-26_simulations_sparseBMA1/sim_result2"
rpath3 = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-09-26_simulations_sparseBMA1/sim_result2"
num_region = 4
side = 64
region_idx = vector("list",num_region)
grids = GP.generate.grids(d=2L,num_grids=side)
grids = as.data.frame(grids)
library(ggplot2)
library(viridis)
source("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/Soft_thresholding/STGP_code/Mediation_Analysis/BMA_pkg/R/MA_data_generation.R", echo=TRUE)
idx_mat = matrix(1:(side*side),ncol = num_region)
idx_matr = matrix(1:(side*side),ncol = 64)
p_length = NULL
region_idx[[1]] = intersect(idx_matr[1:32,],idx_mat[,1:2])
region_idx[[2]] = intersect(idx_matr[33:64,],idx_mat[,1:2])
region_idx[[3]] = intersect(idx_matr[1:32,],idx_mat[,3:4])
region_idx[[4]] = intersect(idx_matr[33:64,],idx_mat[,3:4])
basis_sq = generate_sq_basis(grids, region_idx,a = 0.01,b = 10)
apath = "/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations"
result1 <- readRDS(file.path(apath,"2021-09-24_simulations_denseBMA1/analysis_result_SME.rds"))
result2 <- readRDS(file.path(apath,"2021-09-26_simulations_sparseBMA1/analysis_result_SME2.rds"))
result3 <- readRDS(file.path(apath,"2021-10-08_simulations_dense_4regions/analysis_result_SME4.rds"))
result3_2 <- readRDS(file.path(apath,"2021-10-08_simulations_dense_4regions/sim_result4_2/analysis_result_SME4_2.rds"))
result3_3 <- readRDS(file.path(apath,"2021-10-08_simulations_dense_4regions/analysis_result_SME4_3.rds"))
datsim = readRDS(file.path(dpath,"data1.rds"))
datsim2 = readRDS(file.path(dpath2,"data1.rds"))
datsim3 = readRDS(file.path(dpath3,"data1.rds"))
datsim4 = readRDS(file.path(dpath4,"data1.rds"))
datsim4_3 = readRDS(file.path(dpath4_3,"data1.rds"))
```


For the dense case, FDR is tuned at 0.25 (beta), 0.2(alpha), 0.1(total).

For the sparse case, FDR is tuned at 0.2 (beta), 0.2(alpha), 0.1(total).

For the dense2 case, FDR is tuned as small as possible (before threshold gets too large
and all pixels are mapped to 0.)

For dense2 case, matern kernel is used.

# Main result: Spatial Mediation Effect (SME)
```{r}
dense = result1$sum_SME
dense2 = result3$sum_SME
dense2_2 = result3_2[,1:5]
dense2_3 = result3_3[,1:5]
ana_names = c("dense","sparse","dense2","dense2","dense2")
tab_sme = matrix(NA,nrow=5,ncol=5)
colnames(tab_sme) = colnames(dense)
rownames(tab_sme) = ana_names
dat_param = matrix(NA,nrow=5,ncol=3)
colnames(dat_param) = c("n","sigma_M","sigma_Y")
rownames(dat_param) = ana_names
dat_param[1,] = c(length(datsim$Y), datsim$sigma_m, datsim$sigma_y)
dat_param[2,] = c(length(datsim2$Y), datsim2$sigma_m, datsim2$sigma_y)
dat_param[3,] = c(length(datsim3$Y), datsim3$sigma_m, datsim3$sigma_y)
dat_param[4,] = c(length(datsim4$Y), datsim4$sigma_m, datsim4$sigma_y)
dat_param[5,] = c(length(datsim4_3$Y), datsim4_3$sigma_m, datsim4_3$sigma_y)

tab_sme[1,] = round(apply(dense,2,mean), digits=4)
sparse = result2$sum_SME
tab_sme[2,] = round(apply(sparse,2,mean), digits=4)
tab_sme[3,] = round(apply(dense2,2,mean), digits=4)
tab_sme[4,] = round(apply(dense2_2,2,mean), digits=4)
tab_sme[5,] = round(apply(dense2_3,2,mean), digits=4)
knitr::kable(cbind(dat_param,tab_sme))

```

# Some plots on the dense2 case.

## True images

```{r}
ggplot(grids) + geom_point(aes(x1, x2, color = datsim4$alpha_test_ST),shape=15,size=2) + scale_color_viridis()
ggplot(grids) + geom_point(aes(x1, x2, color = datsim4$beta_test_ST),shape=15,size=2) + scale_color_viridis()
datsim4$total_test_ST = datsim4$beta_test_ST * datsim4$alpha_test_ST
ggplot(grids) + geom_point(aes(x1, x2, color = datsim4$total_test_ST),shape=15,size=2) + scale_color_viridis()
```

## Example posterior sample for dense2, n=1000

```{r}
L_vec = ceiling(unlist(lapply(region_idx, length))*0.2)
  basis_sq = readRDS("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/matern_basis.rds")
Y_result <- readRDS("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_2/simy1.rds")
n_mcmc = dim(Y_result$theta_beta_mcmc_thin)[2]
  theta_sample = Y_result$theta_beta_mcmc_thin[,ceiling(n_mcmc*0.8):n_mcmc]
  beta_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_beta = apply(beta_sample,1,mean)
  grids = as.data.frame(grids)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_beta),shape=15,size=2) + scale_color_viridis()
M_result = M_result <- readRDS("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_2/simm1.rds")
  n_mcmc = dim(M_result$theta_alpha_mcmc)[2]
  theta_sample = M_result$theta_alpha_mcmc[,ceiling(n_mcmc*0.9):n_mcmc]
  alpha_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_alpha = apply(alpha_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_alpha),shape=15,size=2) + scale_color_viridis()
  
  total_sample1 = beta_sample[,1]*alpha_sample[,1]
  ggplot(grids) + geom_point(aes(x1, x2, color = total_sample1 ),shape=15,size=2) + scale_color_viridis()
```

## Example posterior sample for dense2, n=5000

```{r}
Y_result <- readRDS("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_3/simy1.rds")
n_mcmc = dim(Y_result$theta_beta_mcmc_thin)[2]
  theta_sample = Y_result$theta_beta_mcmc_thin[,ceiling(n_mcmc*0.8):n_mcmc]
  beta_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_beta = apply(beta_sample,1,mean)
  grids = as.data.frame(grids)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_beta),shape=15,size=2) + scale_color_viridis()
M_result = M_result <- readRDS("/Volumes/GoogleDrive/My Drive/Research/Bayesian Mediation Analysis/2021_BMA_cleaned/simulations/2021-10-08_simulations_dense_4regions/sim_result4_3/simm1.rds")
  n_mcmc = dim(M_result$theta_alpha_mcmc)[2]
  theta_sample = M_result$theta_alpha_mcmc[,ceiling(n_mcmc*0.9):n_mcmc]
  alpha_sample = STGP_mcmc(theta_sample,region_idx,basis_sq,lambda = datsim$lambda)
  pos_mean_alpha = apply(alpha_sample,1,mean)
  ggplot(grids) + geom_point(aes(x1, x2, color = pos_mean_alpha),shape=15,size=2) + scale_color_viridis()
  
  total_sample1 = beta_sample[,1]*alpha_sample[,1]
  ggplot(grids) + geom_point(aes(x1, x2, color = total_sample1 ),shape=15,size=2) + scale_color_viridis()
```

